### 2021-04-14 paper.Rmd
add reference to huber plot

When using a tour, a sequence of $d$-dimensional linear projections are obtained from a $p$-dimensional space, where $d \ll p$. Let $X_{n \times p}$ be the data matrix, consisting of $n$ observations and $p$ variables, whose projections are of interest. A projection basis, $A_{p \times d}$, is matrix that characterizes the direction from which the data are projected and needs to satisfy an orthonormality condition, which requires that each column in $A$ has unit length and are perpendicular. <!-- This condition gives the $p$-dimensional basis space a geometrical structure of a Stiefel manifold. (Not sure this adds anything) --> With a data matrix and a projection basis, a projection of the data can be defined as $Y = X \cdot A$. Figure \ref{fig:notation-huber} shows an example of lower dimensional projections of the palmer penguins data in a Huber plot and a histogram [@penguins].

>>>>

When using a tour, a sequence of $d$-dimensional linear projections are obtained from a $p$-dimensional space, where $d \ll p$. Let $X_{n \times p}$ be the data matrix, consisting of $n$ observations and $p$ variables, whose projections are of interest. A projection basis, $A_{p \times d}$, is matrix that characterizes the direction from which the data are projected and needs to satisfy an orthonormality condition, which requires that each column in $A$ has unit length and are perpendicular. <!-- This condition gives the $p$-dimensional basis space a geometrical structure of a Stiefel manifold. (Not sure this adds anything) --> With a data matrix and a projection basis, a projection of the data can be defined as $Y = X \cdot A$. Figure \ref{fig:notation-huber} shows an example of lower dimensional projections of the palmer penguins data in a Huber plot and a histogram [@huber1990;@penguins].
